### 2022-05-06 paper/ase22/tables/test-results-table.tex
edit exp & table
revise table

\begin{adjustbox}{angle=90}
\begin{tabular}{p{5cm}||ccccccc}

@@

\tLc & \tNumBlSents & \tNumBlFail & \tNumSeeds & \tNumSeedFail & \tNumExps & \tNumExpFail & \tNumPasstoFail\\

@@

\multirow{3}{*}{\parbox{5cm}{LC1: \UseMacro{test-results-lc0}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc0-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc0-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc0-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc0-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc0-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC2: \UseMacro{test-results-lc1}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc1-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc1-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc1-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc1-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc1-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC3: \UseMacro{test-results-lc2}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc2-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc2-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc2-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc2-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc2-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC4: \UseMacro{test-results-lc3}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc3-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc3-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc3-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc3-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc3-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC5: \UseMacro{test-results-lc4}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc4-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc4-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc4-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc4-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc4-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC6: \UseMacro{test-results-lc5}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc5-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc5-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc5-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc5-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc5-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC7: \UseMacro{test-results-lc6}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc6-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc6-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc6-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc6-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc6-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC8: \UseMacro{test-results-lc7}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc7-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc7-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc7-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc7-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc7-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC9: \UseMacro{test-results-lc8}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc8-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc8-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc8-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc8-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc8-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{5cm}{LC10: \UseMacro{test-results-lc9}}}

@@

 & Model1$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc9-num-seed-fail}

@@

 & Model1$\colon$\UseMacro{test-results-model0-lc9-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc9-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc9-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc9-num-pass-to-fail}\\

@@

\end{tabular}
\end{adjustbox}

>>>>

\resizebox{\textwidth}{!}{
\begin{tabular}{p{4cm}||p{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}p{2cm}}

@@

\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.4cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.3cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC1: \UseMacro{test-results-lc0}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc0-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc0-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc0-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC2: \UseMacro{test-results-lc1}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc1-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc1-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc1-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC3: \UseMacro{test-results-lc2}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc2-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc2-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc2-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC4: \UseMacro{test-results-lc3}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc3-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc3-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc3-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC5: \UseMacro{test-results-lc4}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc4-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc4-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc4-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC6: \UseMacro{test-results-lc5}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc5-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc5-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc5-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC7: \UseMacro{test-results-lc6}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc6-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc6-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc6-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC8: \UseMacro{test-results-lc7}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc7-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc7-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc7-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC9: \UseMacro{test-results-lc8}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc8-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc8-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc8-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-pass-to-fail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC10: \UseMacro{test-results-lc9}}}

@@

 & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc9-num-seed-fail}

@@

 & BERT$\colon$\UseMacro{test-results-model0-lc9-num-exp-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc9-num-pass-to-fail}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-pass-to-fail}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-pass-to-fail}\\

@@

\end{tabular}}
